Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-10-11 manuscript/main.tex
rework sentence

Given that the development of different domains of cognitive function
(e.g., gross motor development vs visual perception) may develop at different times
and be affected by different molecular signals,
we sought to determine whether the associations of microbial taxa
with cognitive function are general across all cognitive subdomains.
To accomplish this, we assessed individual subscales of the  
MSEL (birth to 36 months - \textit{see Methods}). 
Taxonomic profiles coupled with demographics exhibited predictive potential towards three
of five probed subscales (Figure 4A, Table 5), 
namely expressive language ( test-set RMSE 12.05, test-set correlation 0.368), 
gross motor (test-set RMSE 11.07, test-set correlation 0.137) and 
visual reception (test-set RMSE 15.2, test-set correlation 0.333).
Between the subscales, not only the predictability (measured by the test-set figures of merit) is different,
but also the relative importances of several taxa (Figure 4B).
Although certain species such as \textit{B. longum}, \textit{F. prausznitzii} 
have similar relative importance across all subscales, others are substantially different (Tables S2-S4).
Notably, \textit{Bifidobacterium pseudocatenulatum}, \textit{B. wexlerae} and \textit{E. eligens} are
substantially more important for the prediction of expressive language, while
\textit{R. faecis}, \textit{Streptococcus salivarius} and \textit{Fusicatenibacter saccharivorans} are
distinctly predictive of gross motor, and
\textit{Clostridium innocuum}, \textit{B. vulgatus} 
stand out on models targeting visual reception (Supplenmentary Tables S2-4).

>>>>

Given that the development of different domains of cognitive function
(e.g., gross motor development vs visual perception) may develop at different times
and be affected by different molecular signals,
we sought to determine whether the associations of microbial taxa
with cognitive function are general across all cognitive subdomains.
To accomplish this, we assessed individual subscales of the  
MSEL (birth to 36 months - \textit{see Methods}). 
Taxonomic profiles coupled with demographics exhibited predictive potential towards three
of five probed subscales (Figure 4A, Table 5), 
namely expressive language ( test-set RMSE 12.05, test-set correlation 0.368), 
gross motor (test-set RMSE 11.07, test-set correlation 0.137) and 
visual reception (test-set RMSE 15.2, test-set correlation 0.333).
Between the subscales, both the predictability (measured by the test-set figures of merit)
and the relative importances of several taxa (Figure 4B) is variable.
Although certain species such as \textit{B. longum}, \textit{F. prausznitzii} 
have similar relative importance across all subscales, others are substantially different (Tables S2-S4).
Notably, \textit{Bifidobacterium pseudocatenulatum}, \textit{B. wexlerae} and \textit{E. eligens} are
substantially more important for the prediction of expressive language, while
\textit{R. faecis}, \textit{Streptococcus salivarius} and \textit{Fusicatenibacter saccharivorans} are
distinctly predictive of gross motor, and
\textit{Clostridium innocuum}, \textit{B. vulgatus} 
stand out on models targeting visual reception (Supplenmentary Tables S2-4).
